This is an example of article title

### 2025-10-28 paper/paper.tex
Add a todo to discuss.
remove unnecessary character

Note that while the group action $\sigma(g, \sigmaæ(h, p)) = \sigma(g \cdot h, p)$ “appends” a new action (w.r.t.~$g$) on the left, for the inverse we have
\begin{align*}
        \sigma^{-1}(g, \sigma^{-1}(h, p))
        &= \sigma(g^{-1}\cdot h^{-1}, p)
        = \sigma((h \cdot g)^{-1}, p)
        \\
        &= \sigma^{-1}(h \cdot g, p)
\end{align*}
for all \(g, h \in \mathcal{G}\). This is a so-called right action.
Similarly for a right group action the inverse is a left group action.
This is tanken into account when using \verb|apply|.

@@

\section{An example how to use {\texttt{LieGroups.jl}}}\label{sec:Example}

{\color{red}TODO: Brainstorm over one or two examples with code.}
\input{bib.tex}
\end{document}
%
% ------------------------------------------------------------------------------------------
%

>>>>

Note that while the group action $\sigma(g, \sigma(h, p)) = \sigma(g \cdot h, p)$ “appends” a new action (w.r.t.~$g$) on the left, for the inverse we have
\begin{align*}
        \sigma^{-1}(g, \sigma^{-1}(h, p))
        &= \sigma(g^{-1}\cdot h^{-1}, p)
        = \sigma((h \cdot g)^{-1}, p)
        \\
        &= \sigma^{-1}(h \cdot g, p)
\end{align*}
for all \(g, h \in \mathcal{G}\). This is a so-called right action.
Similarly for a right group action the inverse is a left group action.
This is tanken into account when using \verb|apply|.

@@

\section{An example how to use {\texttt{LieGroups.jl}}}%
\label{sec:Example}

{\color{red}TODO: Brainstorm over one or two examples with code.}

\input{bib.tex}
\end{document}
%
% ------------------------------------------------------------------------------------------
%
